---
title: "ADS"
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
wk1.date <- as.Date("2022-01-24")
```

This is the course website for <span style="color:blue">**MATH 485 - Advanced Data Science**</span> course taught by [Dr. Robin Donatello](www.norcalbiostat.com) in Spring 2022 at California State University, Chico. This landing page is used for posting of regular announcements and information for students of the class. 

_This course aims to help students navigate the evolving and murky waters of the Data Science landscape. We do so by not only providing training in advanced programming and technical skills, but also by providing opportunities for collaboration with other disciplines and reflection on how Data Science impacts human society._

----
_Last Updated: `r format(Sys.time(), "%a %b %d %X")`_

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(kableExtra);
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# Schedule  {.tabset .tabset-fade .tabset-pills}

[Google Calendar view](https://calendar.google.com/calendar/u/0?cid=bWFpbC5jc3VjaGljby5lZHVfajg0NjlvamVhcHFyZXNiZWswdmxobzRxMjBAZ3JvdXAuY2FsZW5kYXIuZ29vZ2xlLmNvbQ)

## Weekly Overview 

```{r}
# Read in schedule
raw_detail <- read_excel("schedule_485.xlsx", sheet="schedule")

cdat <- raw_detail %>% mutate(Date = format(date, "%m/%d"))

#cdat$Assignments <- gsub(" (", " <b> (", cdat$Assignments, fixed=TRUE)
#cdat$Assignments <- gsub(" )", ")</b>", cdat$Assignments, fixed=TRUE)
```

```{r, results='asis', echo=FALSE, message=FALSE, warning=FALSE}
out <- cdat %>% select(Week, Date, Topic, `Learning Objectives` = SLO, Prepare)

knitr::kable(out, align="cclll", escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered"), 
                position='center') %>% 
  column_spec(1, width="5%") %>% 
  column_spec(2, width="5%") %>% 
  column_spec(3, width="20%") %>% 
  column_spec(4, width="30%") %>% 
  column_spec(5, width="20%") 
```


## Deliverables

_Todo: Display as DT so can filter on week or due date._

```{r}
tasks <- read_xlsx("C:/GitHub/ADS/schedule_485.xlsx", sheet = "assignments", 
          col_types = c("numeric", "numeric", "text", "text", "text", 
                        "text", "date", "numeric"))

tasks %>% 
  filter(!is.na(order)) %>%
  select(-order, -pct_effort) %>% 
  kable(align="l", escape=FALSE) %>% 
   kable_styling(bootstrap_options = c("hover", "striped", "responsive", "bordered"), 
                position='center') %>% 
  column_spec(1, width="5%") %>% 
  column_spec(2, width="10%") %>% 
  column_spec(3, width="30%") %>% 
  column_spec(4, width="5%") %>%
  column_spec(5, width="10%")  %>%
  column_spec(6, width="5%")
```

<!---
### `r format(wk1.date+2*7, "%m-%d-%Y")` Week 3: Project Introductions

On Tuesday you will get back to coding and work through a case study out of DDS Ch 2, then get an introduction to the consulting projects you will be working on throughout the semester. 

The weekly content pages have been added to the navigation bar. I really ought to convert this page over to a distill based site. 

----

### `r format(wk1.date+1*7, "%m-%d-%Y")` Week 2: What is Data Science? 

#### Housekeeping
* Updates to schedule page
    - New tab that lists all deliverables
    - Order listed is order of introduction NOT order of due date. 
    - Always subject to change as our pace through the material changes

#### This week

* Websites
    - We'll finish our introduction to working with `blogdown` to make dynamic websites. 
    - Then you need to start working on creating your own personal page. 

* What is Data Science
    - We'll explore the world of DS a bit more in depth, using HackMD as a place for our collaborative notes.
    - Read DDS Ch 1 and 16 to provide background and context

* Finding your DS Niche? 
    - What is your skillset? Your domain? 
    - Where do you want to grow? 


----

### `r format(wk1.date, "%m-%d-%Y")` Week 1: Welcome to Spring 22!

This course website contains all materials except the textbooks for this class. Be sure to familiarize yourself with the organization. You will be here a lot. Bookmark this page.

This week we will make sure you are connected to all the content and platforms for the class, and start working to build your first website using R & Markdown.

