---
title: "ADS"
output: html_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
wk1.date <- as.Date("2022-01-24")
```

This is the course website for <span style="color:blue">**MATH 485 - Advanced Data Science**</span> course taught by [Dr. Robin Donatello](www.norcalbiostat.com) in Spring 2022 at California State University, Chico. This landing page is used for posting of regular announcements and information for students of the class. 

_This course aims to help students navigate the evolving and murky waters of the Data Science landscape. We do so by not only providing training in advanced programming and technical skills, but also by providing opportunities for collaboration with other disciplines and reflection on how Data Science impacts human society._

----
_Last Updated: `r format(Sys.time(), "%a %b %d %X")`_

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(kableExtra)
options(knitr.table.format = "html", knitr.kable.NA = '') 
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE) 
```

# Schedule  {.tabset .tabset-fade .tabset-pills}

[Google Calendar view](https://calendar.google.com/calendar/u/0?cid=bWFpbC5jc3VjaGljby5lZHVfajg0NjlvamVhcHFyZXNiZWswdmxobzRxMjBAZ3JvdXAuY2FsZW5kYXIuZ29vZ2xlLmNvbQ)

## Weekly Overview 

```{r}
# Read in schedule
sched <- read_excel("schedule_485.xlsx", sheet="schedule") %>% 
  mutate(Date = format(date, "%m/%d")) %>% 
  select(Week, Date, Topic, `Learning Objectives` = SLO, Prepare)

tasks <- read_xlsx("C:/GitHub/ADS/schedule_485.xlsx", sheet = "assignments", 
          col_types = c("numeric", "numeric", "text", "text", "text", 
                        "text", "date", "numeric")) %>%
  mutate(due_date = format(due_date, "%m/%d"))


wk.col <- "background-color: #86511D; color: #fff;"

```

```{r}
sched %>%
  kbl(align="lclll", escape=FALSE) %>%
  kable_paper("hover", full_width=F, html_font = "Ariel",
              position='center', font_size=14) %>%
  column_spec(1, width="5%") %>% 
  column_spec(2, width="5%", border_right = TRUE) %>% 
  column_spec(3, width="20%") %>% 
  column_spec(4, width="35%") %>% 
  column_spec(5, width="35%") %>%
  pack_rows("Week 1", 1,2, label_row_css = wk.col) %>%
  pack_rows("Week 2", 3,3, label_row_css = wk.col) %>%
  pack_rows("Week 3", 4,5, label_row_css = wk.col) %>%
  pack_rows("Week 4", 6,7, label_row_css = wk.col) %>%
  pack_rows("Week 5", 8,10, label_row_css = wk.col) %>%
  pack_rows("Week 6", 11,13, label_row_css = wk.col) %>%
  pack_rows("Week 7", 14,16, label_row_css = wk.col) %>%
  pack_rows("After Spring Break", 17,NROW(sched), label_row_css = wk.col)

```


## Deliverables

```{r}



tasks %>%
  filter(!is.na(order)) %>%
  select(-order, -pct_effort, -week, Due=due_date) %>%
  kbl(align="llclc", escape=FALSE) %>%
  kable_paper("hover", full_width=F, html_font = "Ariel",
              position='center', font_size=14) %>%
  column_spec(1, width="10%") %>%
  column_spec(2, width="25%") %>%
  column_spec(3, width="5%") %>%
  column_spec(4, width="15%")  %>%
  column_spec(5, width="5%") %>%
  pack_rows("Week 1", 1,9, label_row_css = wk.col) %>%
  pack_rows("Week 2", 10,17, label_row_css = wk.col) %>%
  pack_rows("Week 3", 18,19, label_row_css = wk.col) %>%
  pack_rows("Week 4", 20,22, label_row_css = wk.col) %>%
  pack_rows("Week 5", 23,26, label_row_css = wk.col) %>%
  pack_rows("Week 6", 27,30, label_row_css = wk.col) %>%
  pack_rows("Week 7", 31,30, label_row_css = wk.col)
```



