---
title: "Course materials"
output: html_document
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr); library(dplyr);library(pander)
```


# Lecture Notes
```{r, message=FALSE, warning=FALSE, echo=FALSE}
lec <- data.frame(filenames = paste0('lec/', list.files("lec", pattern='*.pdf|*.html|*.docx')))

out.lec <- lec %>% mutate(name = gsub("lec/|.html|.pdf|.md",  "", filenames), 
                          link = sprintf("[%s](%s)",name, filenames))
pander(as.list(out.lec$link))
```

**Collaborative Notes on HackMD**

* [lec02-what-is-ds](https://hackmd.io/@norcalbiostat/data485-lec02) 
* [Getting historical data out of twitter](https://hackmd.io/@norcalbiostat/data485-twitter) (part of hw03)
* [Real Estate Website Case Study](https://hackmd.io/@norcalbiostat/real-estate-case-study) (part of hw04)
* [lec03_classifiers](https://hackmd.io/@norcalbiostat/lec03_classifiers)


# Homework 
```{r, message=FALSE, warning=FALSE, echo=FALSE}
hw <- data.frame(filenames = paste0('hw/', list.files("hw", pattern='*.pdf|*.html|*.docx')))

out.hw <- hw %>% mutate(name = gsub("hw/|_template",  "", filenames), 
                          type = str_extract(hw$filenames,".{3}$"),
                          type = ifelse(type=="tml", "html", type),
                          type = ifelse(type=="ocx", "docx", type),
                          nam = gsub(".html|.pdf|.Rmd|.docx", "", name), 
                          link = sprintf("[%s](%s)",nam, filenames))
pander(as.list(out.hw$link))
```

# Reading
```{r, message=FALSE, warning=FALSE, echo=FALSE}
read <- data.frame(filenames = paste0('read/', list.files("read", pattern='*.pdf|*.html|*.docx')))
out.read <- read %>% mutate(name = gsub("read/",  "", filenames), 
                            name = gsub(".pdf", "", name),
                            link = sprintf("[%s](%s)",name, filenames))


pander(as.list(out.read$link))
```

Supplemental material for ISLR: 

* Slides and videos for Statistical Learning MOOC by Hastie and Tibshirani:  http://auapps.american.edu/alberto/www/analytics/ISLRLectures.html 
* Slides and video tutorials related to this book by Abass Al Sharif: https://www.alsharif.info/iom530 


# Other Books on Data Science
Note - many of these books are links to a Tweet where the book is promoted/discussed. I leave the tweets in there so you can 1) see the entire context of the post, and 2) you can learn more people involved in the DS world that you may want to follow. 

* DS with R - Garrett Grolemund https://garrettgman.github.io/
* Another book on Data Science https://www.anotherbookondatascience.com/
* Text mining with R https://www.tidytextmining.com/
* Create your own DS curriculum https://twitter.com/DataKimist/status/1213855599013830657?s=09
* "Best Free Data Science ebook" https://twitter.com/kareem_carr/status/1205191083443048448?s=09
* Building a career in Data Science https://twitter.com/skyetetra/status/1202350563859369984?s=09
    - might be same book https://twitter.com/robinson_es/status/1207450496019111942?s=09
* How to be a modern scientist https://twitter.com/alexpghayes/status/1200917769774141442?s=09    


# Other books on Ethics & Algorithms

* [Race after techcnology: Abolistionist tools for the new Jim Code](https://www.amazon.com/Race-After-Technology-Abolitionist-Tools/dp/1509526404). 
* [When Data Science Destabilizes Democracy and Facilitates Genocide](http://www.fast.ai/2017/11/02/ethics/)
* [Activision Patents Matchmaking That Encourages Players To Buy Microtransactions](https://kotaku.com/activision-patents-matchmaking-that-encourages-players-1819630937)
* [More than a Million Pro-Repeal Net Neutrality Comments were Likely Faked](https://hackernoon.com/more-than-a-million-pro-repeal-net-neutrality-comments-were-likely-faked-e9f0e3ed36a6)

