---
output:
  html_document:
    toc: yes
    toc_float: yes
    css: style.css
title: "Week 4: Feb 13 - Feb 19"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr);library(readxl); library(knitr)
library(kableExtra); library(stringr)
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```
_Last Updated: `r format(Sys.time(), "%a %b %d %X")` _


```{r echo=FALSE, message=FALSE, warning=FALSE}
raw <- read_excel("schedule_485.xlsx")
week.w <- filter(raw, Week==4)

SLO    <- t(str_split(week.w$SLO, "\r\n", simplify=TRUE))
prep   <- t(str_split(week.w$Prepare, "\r\n", simplify=TRUE))
refs   <- t(str_split(week.w$References, "\r\n", simplify=TRUE))
hw     <- t(str_split(week.w$Assignments, "\r\n", simplify=TRUE))
topic1 <- t(str_split(week.w$Topic1, "\r\n", simplify=TRUE))
topic2 <- t(str_split(week.w$Topic2, "\r\n", simplify=TRUE))
```

----

# Learning Objectives
```{r}
kable(SLO) %>% kable_styling(bootstrap_options = c("striped","condensed"))
```

----

# Prepare
```{r}
kable(prep) %>% kable_styling(bootstrap_options = c("striped","condensed"))
```

----

# References
```{r}
kable(refs) %>% kable_styling(bootstrap_options = c("striped","condensed"))
```

----

# Topics

```{r}
kable(topic1) %>% kable_styling(bootstrap_options = c("striped","condensed"))
```


### Method of Least Squares 

Consider the following linear model with $p$ predictors and where $\beta_{1}= \mathbf{1}$ (the $nx1$ intercept vector containing all 1s): 

$$
y_{ij} = \sum_{i=1}^{n} X_{ij}\beta_{j} \qquad j=1, \ldots, p
$$

This can also be written as $y_{ij} = \mathbf{X}\beta$. The best fit line is the set of $\beta$'s that minimizes the squared residuals, or distances, between the predicted value $\mathbf{X}\beta$ and observed value $y_{ij}$. That means we need to minimize this: 

$$
\lVert y-\mathbf{X}\beta \rVert^{2}
$$
Given that the columns of $\mathbf{X}$ are linearly independent ($cov(x_{j}, x_{j^{'}})=0$), there is a [[unique solution]](https://en.wikipedia.org/wiki/Linear_least_squares_(mathematics)#Derivation_of_the_normal_equations) to this problem. 

$$
\hat{\mathbf{\beta}}=(\mathbf{X}^{T}\mathbf{X})^{-1}\mathbf{X}^{T}\mathbf{y} 
$$

This is why we care about multicollinearity and sparseness. If one variable is an exact linear function of another then $\mathbf{X}^{T}\mathbf{X}$ is not positive definite, and thus not invertable. 

An example of this is in the case of a rare event. The column containing an indicator for that event would be nearly perfectly collinear with the intercept, causing algebraic inversion properties (or quasi-complete separation). 


----

# Assignments
```{r}
kable(hw) %>% kable_styling(bootstrap_options = c("striped","condensed"))
```
