---
title: 'Text analysis on project data'
author: "Student name"
output: html_document
---

# Instructions
 
1. Change the author name and give it a more meaningful title that reflects your project 
2. Download your project data from Google Drive and place into the `data` folder. This has been added to your `.gitignore` so that it will not upload to GitHub. 
3. Make sure you have the libraries listed below installed.
4. Knit this document to HTML or PDF prior to submission. 

> Always remove any instructional text before submission. 


```{r, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse)
library(tidytext)
library(wordcloud)
```


# Project objective
> Describe your project objective here as it relates to topic sentiment. If your research group does not have a research question directly tied to a sentiment, make one up. That is, look at what your group is researching, and ask yourself if you can add to the story using sentiments. 

# Data import and cleaning 
> Import your project topic data set. 
> Apply any filters that are appropriate for your project. 
> Tidy your text


# Visualize word frequency
> Create two plots, side by side with the count on the left, the proportion on the right. 
> These could be all words, hashtags, usernames, ... your choice. 
> Find a categorical variable that is of potential interest for your research project. Use tidytext principles to `spread` the word frequencies (as a proportion) across categories (converting long to wide). Create a 'scatterplot' of words similar to Figure 1.3 in the Text mining book. 



# Applying Sentiments
> Talk with your group and decide on the method of sentiment application you wish to use. 
> Apply this chosen sentiment application (or choose one for them if you're not hearing back)
> Pick an exploratory technique from Text Mining in R Chapter 2.4-2.6 and apply it here. 


----
_Last compiled on `r Sys.time()`_.
```{r}
sessionInfo()
```

